Preparing and submitting articles for the Archive of Numerical Software

### 2011-05-16 submitting.tex
add bibliography
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@2683 a653633e-0a08-0410-9ecb-ed4064e9718a

\section{Testing some code}

\begin{c++}
// Get dimensions of local mesh_data
const uint num_local_cells = mesh_data.cell_vertices.size();
assert(global_cell_indices.size() == num_local_cells);
const uint num_cell_vertices = mesh_data.cell_vertices[0].size();

// Build array of cell-vertex connectivity and partition vector
std::vector<uint> cell_vertices;
std::vector<uint> cell_vertices_partition;
const uint size = num_local_cells*(num_cell_vertices + 1);
cell_vertices.reserve(size);
cell_vertices_partition.reserve(size);
for (uint i = 0; i < num_local_cells; i++)
{
  cell_vertices.push_back(global_cell_indices[i]);
  cell_vertices_partition.push_back(cell_partition[i]);
  for (uint j = 0; j < num_cell_vertices; j++)
  {
    cell_vertices.push_back(mesh_data.cell_vertices[i][j]);
    cell_vertices_partition.push_back(cell_partition[i]);
  }
}

@@

\begin{python}
# Time-stepping
t = dt
p = Progress("Time-stepping")
while t < T + DOLFIN_EPS:

@@

\end{document}

>>>>

\section{Code samples}

All code listings are based on the \texttt{listings}
package~\cite{HeinzMoses07}.  The style file \texttt{anslistings.sty},
automatically included by \texttt{ansarticle.cls}, provides standard
styles for a variety of common programming languages. Changing any
listing style parameters is not encouraged and may lead to unexpected
outcomes in the final publication.

Below, we provide samples of listings for the languages available. If
a language is missing, please contact the managing editor for an
updated style file.

\subsection{C++}

C++ code should be compliant with the current C++ standard. Two
commands are provided to prettyprint C++ code. First, an environment
to put C++ code into the LaTeX file, namely

\begin{latexcode}
\begin{c++}
  // Your C++ code here
\end{c++}
\end{latexcode}

Alternatively, it is possible to use \lstinline[language=TeX]!\inputcpp{file.cc}!
to print the C++ code in a file. Here is an example what C++ code
looks like.

\begin{c++}
// Get dimensions of local mesh_data
const unsigned int num_local_cells = mesh_data.cell_vertices.size();
assert(global_cell_indices.size() == num_local_cells);
const unsigned int num_cell_vertices = mesh_data.cell_vertices[0].size();

// Build array of cell-vertex connectivity and partition vector
std::vector<unsigned int> cell_vertices;
std::vector<unsigned int> cell_vertices_partition;
const unsigned int size = num_local_cells*(num_cell_vertices + 1);
cell_vertices.reserve(size);
cell_vertices_partition.reserve(size);
for (unsigned int i = 0; i < num_local_cells; i++)
{
  cell_vertices.push_back(global_cell_indices[i]);
  cell_vertices_partition.push_back(cell_partition[i]);
  for (unsigned int j = 0; j < num_cell_vertices; j++)
  {
    cell_vertices.push_back(mesh_data.cell_vertices[i][j]);
    cell_vertices_partition.push_back(cell_partition[i]);
  }
}

@@

\subsection{Python}
\begin{python}
# Time-stepping
t = dt
p = Progress("Time-stepping")
while t < T + DOLFIN_EPS:

@@

\bibliographystyle{abbrv}
\bibliography{submitting}
\end{document}
